Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
revision sec 4.5

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. It does this by assuming a plan't
precision $<I_p,F_p>$, a $k$ and a sampling rate.  The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.

2. The validation phase consists of four stages (blocks 2-5 in
Fig.~\ref{fig:CEGIS-precision-increment}), where the first one
performs potentially unsound operations considering the currently
assumed plant's precision $<I_p,F_p>$, $k$ and sampling rate, whereas
the subsequent three stages are used to restore soundness.

3. This stage restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage.

4. This stage checks that the current  $k$ 
is large enough to ensure that the boundaries are not violated for any $k'>k$.
In order to verify this, we compute the 
completeness threshold $\overline{k}$ for the current candidate $K$ 
and check that $k{\leq}\overline{k}$. 
\todo{discuss the computation of the completeness threshold}

5. The last stage ensures that the current sampling rate is large enough by using an 
external checker (\todo{add more details here once we have them}).

>>>>

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. It does this by assuming some 
precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The checks that
these assumptions are sound are performed by the subsequent {\sc
  verify} stages.

2. The first {\sc verify} stage, {\sc safety}, 
performs potentially unsound operations by considering the currently
assumed $<I_p,F_p>$, $k$ and sampling rate. % The soundness is to be 
% restored by the subsequent three validation stages.

3. The second {\sc verify} stage, {\sc precision}, 
 restores soundness with respect to the plant's precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage.

4. The third {\sc verify} stage, {\sc complete}, checks that the
current $k$ is large enough to ensure that the boundaries are not
violated for any $k'>k$.  For this purpose, we compute the
completeness threshold $\overline{k}$ for the current candidate $K$
and check that $k{\leq}\overline{k}$.  \todo{discuss the computation
  of the completeness threshold}

5. The last {\sc verify} stage, {\sc sampling}, 
ensures that the current sampling rate is large enough by using an 
external checker (\todo{add more details here once we have them}).
